|

### 2021-07-20 paper/memo/memo.Rmd
adjust citation

In terms of the impact of measurement error on estimated effects, many studies have shown when taking measurement uncertainty into account, magnitude of coeffients of latent variables can be either attenuated or enlarged substantively [e.g., @treier_democracy_2008, p. 211; @caughey_policy_2018,p. 254].

>>>>

In terms of the impact of measurement error on estimated effects, many studies have shown when taking measurement uncertainty into account, magnitude of coeffients of latent variables can be either attenuated or enlarged substantively [e.g., @Treier2008, p. 211; @caughey_policy_2018,p. 254].
